JSSET: JavaScript Semantics Extraction Toolchain

### 2019-08-15 icse/compiler.tex
Written abstract

In this section, we propose the \textit{algorithm compiler}
that compiles abstract algorithms into \( \ires \) functions
and its overall structure is described in Figure~\ref{fig:algo-compiler}.
Before compiling abstract algorithms,
the tokenizer first tokenizes each abstract algorithm into
a list of tagged tokens. Then, the token parser constructs
syntactic parse tree of the given token list.
Finally, the \( \ires \) function generator constructs the coressponding
\( \ires \) function from the given parse tree.
The parser and the generator is dependent on conversion rules
and we define the general conversion rules for abstract algorithms in
ECMAScript specifications. Like Coq, a proof assistant, we also provide
the \textit{rule generation assistant} to make easy write conversion rules.
It diagnoses root causes of failed parsing tokens
and suggests new conversion rules based on
statistical analysis of algorithm steps that failed to be parsed.

@@

Abstract algorithms in ECMAScript specifications are written in structured
natural languages in HTML files. An algorithm consists of ordered steps
and it might contain sub-steps as well. For example,
the \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es}
has three steps and second step has seven sub-steps.
Moreover, the tokens of each step has its own HTML tag and each tag
has the following meaning:
\[
  \begin{array}{c|l}
    \text{HTML tags} & \text{meanings}\\\hline\hline
    \code{<var>} & \text{variables}\\\hline
    \code{<emu-grammar>} & \text{productions}\\\hline
    \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
    \code{<code>} & \text{ECMAScript codes}\\\hline
    \code{<emu-const>} & \text{constant values}\\\hline
    \code{<emu-val>} & \text{values}\\\hline
    \code{<ol>} & \text{ordered sub-steps}\\\hline
    \code{<ul>} & \text{unordered sub-steps}\\\hline
    \code{<sup>} & \text{superscripts}\\\hline
    \text{otheriwse} & \text{simple texts}\\\hline
  \end{array}
\]
We try to keep the tag information for each token to generate more
precise conversion rules. For example, if and only if a token has a tag
\( \code{<var>} \), it is a parameter or a local variable.
Thus, it is possible to construct a conversion rule precisly discriminates
identifiers and other components.

The tokenizer first recognizes the overall structures of steps.
Then, it divides each step into sequence of tagged tokens.
If an HTML element has a explicit tag, it is converted into a single token
with the tag. Otherwise, it is splitted into multiple tokens and each token
should be a sequence of alphanumeric characters or a single
non-alphanumeric character. For example, in the \( \code{ToPrimitive} \)algorithm,
\( \textbf{\code{"default"}} \) is a single token with the tag \( \code{<code>} \)
and \( \code{@@toPrimitive} \) is splitted into three text tokens
\( \code{@} \), \( \code{@} \), and \( \code{toPrimitive} \).

@@

The token parser parses a given list of tokens into a syntactic parse tree.
It depends on the given \textit{conversion rules} that consists of
two parts parsing rules and mapping from parsing rules into corresponding
\( \ires \) components.
A parsing rule consists of basic token matchers and other parsing rules
including itself. For example, the following parsing rule is simplifed version for
sub-step \( i \) in the \( \code{ToPrimitive} \) algorithm.
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
// expressions
val Expr = (
  // identifiers
  varT ^^ ... |
  // return if abrupt
  "?" ~ Expr ^^ ... |
  // function calls
  textT ~ "(" ~ repsep(varT, ",") ~ ")" ^^ ... |
  // lists
  "<<" ~ repsep(Expr, ",") ~ ">>" ^^ ...
)
\end{lstlisting}

Each parsing rule is written in extended Scala parser combinators.
We modify the meaning of altenative composition operator ( \( | \) ) to collect
all longest matched results. If the parser detects that a step cannot be
parsed with the given parsing rules. It reports that a step is not possible
to be parsed under the given rules into the rule generation assistant.
Moreover, even though the parser could parse a step, it will be also reported
if it could be parsed in not a single but multiple ways.
Each string literal is a token matcher for tokens without any tags and checks
that the token has same string value with the sring literal.
The \( \code{varT} \) and \( \code{textT} \) is also token matchers
for token with the tag \( \code{<var>} \) and no tags.
The \( \code{Step} \) and \( \code{Expr} \) are user-defined parsing rules
defined with our extended parser combinators.
Morevoer, it supports all helpers functions defined in Scala parser combinators.
For example, the helper function \( \code{repsep(p, q)} \) generates a new
parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
using another parsing rule \( \code{q} \) as separators.
Finally, the token parser with the above rules parses sub-step \( i \) in the
\( \code{ToPrimitive} \) into the following syntactic parse tree:
\includegraphics[width=0.5\textwidth]{img/parse_tree.png}

@@

\item \textbf{Imparative Style} \( \ires \) represents algorithm steps
as statements. Each statement changes the current state
that consists of environments and a heap.

\item \textbf{Higher-order Functions with Restricted Scopes} \( \ires \) supports
lambda functions as values but it has only restricted scopes. In each function,
only global variables, parameter, and newly defined local variables are accessible.
It means that the function closure does not capture the the current environemnt.
We use such restricted scopes becuase it is enough to represent abstract algorithms.

\item \textbf{Primitive Values} \( \ires \) supports ECMAScript primitive values except
the symbols that is newly introduced after ECMAScript 6. Thus, only five ECMAScript primitives
are defined in \( \ires \); numbers, strings, booleans, undefined, and null.
Moreover, \( \ires \) also supports the unique \( \code{absent} \) value to represent
the absence of parameters. For example, the second parameter \( \code{PreferredType} \)
of \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es} might be
not present in some function calls. Then, the parameter has the \( \code{absent} \) value
to represent its absence.

\item \textbf{Abstract Data Types} \( \ires \) only supports three abstract data types;
\( \code{Record} \) for mapping from some values into other value,
\( \code{List} \) for sequenital data types,
and \( \code{Singletone} \) for singleton data types.
They are stored in corresponding addresses in the heap structure.
For example, ECMAScript environment records are represented as \( \code{Record} \) data types
from String values for identifier names into addresses.
The addresses point to other \( \code{Record} \) data types that represent ECMAScript bindings.
We treat a ECMAScript constants such as \( \code{empty} \) and primitive symbols as singleton
data types in \( \ires \).
\end{itemize}

@@

To make easy write conversion rules, we support \textit{rule generation assistant}.
It consists of several helper functions to show the specific statistics of
the not yet convertable abstract algorithm steps. It make easy not only construct
conversion reuls from the scratch but also update existing conversion rules
for updated specifications. We explain each helper function and how to utilize
it to construct conversion rules.

@@

\subsubsection{Fault localizations based on \( \tstar \) tokens}

>>>>

In this section, we propose the \textit{algorithm compiler}
that compiles abstract algorithms into \( \ires \) functions
and its overall structure is described in Figure~\ref{fig:algo-compiler}.
Before compiling abstract algorithms,
the tokenizer first tokenizes each abstract algorithm into
a list of tagged tokens. Then, the token parser constructs
syntactic parse tree of the given token list.
Finally, the \( \ires \) function generator constructs the corresponding
\( \ires \) function from the given parse tree.
The parser and the generator is dependent on conversion rules
and we define the general conversion rules for abstract algorithms in
ECMAScript specifications. Like Coq, a proof assistant, we also provide
the \textit{rule generation assistant} to make easy write conversion rules.
It diagnoses root causes of failed parsing tokens
and suggests new conversion rules based on
statistical analysis of algorithm steps that failed to be parsed.

@@

Abstract algorithms in ECMAScript specifications are written in structured
natural languages in HTML files. An algorithm consists of ordered steps
and it might contain sub-steps as well. For example,
the \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es}
has three steps and second step has seven sub-steps.
Moreover, the tokens of each step has its own HTML tag and each tag
has the following meaning:
\[
  \begin{array}{c|l}
    \text{HTML tags} & \text{meanings}\\\hline\hline
    \code{<var>} & \text{variables}\\\hline
    \code{<emu-grammar>} & \text{productions}\\\hline
    \code{<emu-nt>} & \text{non-terminal syntax}\\\hline
    \code{<code>} & \text{ECMAScript codes}\\\hline
    \code{<emu-const>} & \text{constant values}\\\hline
    \code{<emu-val>} & \text{values}\\\hline
    \code{<ol>} & \text{ordered sub-steps}\\\hline
    \code{<ul>} & \text{unordered sub-steps}\\\hline
    \code{<sup>} & \text{superscripts}\\\hline
    \text{otherwise} & \text{simple texts}\\\hline
  \end{array}
\]
We try to keep the tag information for each token to generate more
precise conversion rules. For example, if and only if a token has a tag
\( \code{<var>} \), it is a parameter or a local variable.
Thus, it is possible to construct a conversion rule precisely discriminates
identifiers and other components.

The tokenizer first recognizes the overall structures of steps.
Then, it divides each step into sequence of tagged tokens.
If an HTML element has a explicit tag, it is converted into a single token
with the tag. Otherwise, it is divided into multiple tokens and each token
should be a sequence of alphanumeric characters or a single
non-alphanumeric character. For example, in the \( \code{ToPrimitive} \)algorithm,
\( \textbf{\code{"default"}} \) is a single token with the tag \( \code{<code>} \)
and \( \code{@@toPrimitive} \) is divided into three text tokens
\( \code{@} \), \( \code{@} \), and \( \code{toPrimitive} \).

@@

The token parser parses a given list of tokens into a syntactic parse tree.
It depends on the given \textit{conversion rules} that consists of
two parts parsing rules and mapping from parsing rules into corresponding
\( \ires \) components.
A parsing rule consists of basic token matchers and other parsing rules
including itself. For example, the following parsing rule is simplified version for
sub-step \( i \) in the \( \code{ToPrimitive} \) algorithm.
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = "Let" ~ varT ~ "be" ~ Expr ~ "." ^^ ...
// expressions
val Expr = (
  // identifiers
  varT ^^ ... |
  // return if abrupt
  "?" ~ Expr ^^ ... |
  // function calls
  textT ~ "(" ~ repsep(varT, ",") ~ ")" ^^ ... |
  // lists
  "<<" ~ repsep(Expr, ",") ~ ">>" ^^ ...
)
\end{lstlisting}

Each parsing rule is written in extended Scala parser combinators.
We modify the meaning of alternative composition operator ( \( | \) ) to collect
all longest matched results. If the parser detects that a step cannot be
parsed with the given parsing rules. It reports that a step is not possible
to be parsed under the given rules into the rule generation assistant.
Moreover, even though the parser could parse a step, it will be also reported
if it could be parsed in not a single but multiple ways.
Each string literal is a token matcher for tokens without any tags and checks
that the token has same string value with the string literal.
The \( \code{varT} \) and \( \code{textT} \) is also token matchers
for token with the tag \( \code{<var>} \) and no tags.
The \( \code{Step} \) and \( \code{Expr} \) are user-defined parsing rules
defined with our extended parser combinators.
Moreover, it supports all helpers functions defined in Scala parser combinators.
For example, the helper function \( \code{repsep(p, q)} \) generates a new
parsing rule that denotes zero or more repetitions of the parsing rule \( \code{p} \)
using another parsing rule \( \code{q} \) as separators.
Finally, the token parser with the above rules parses sub-step \( i \) in the
\( \code{ToPrimitive} \) into the following syntactic parse tree:
\includegraphics[width=0.5\textwidth]{img/parse_tree.png}

@@

\item \textbf{Imperative Style} \( \ires \) represents algorithm steps
as statements. Each statement changes the current state
that consists of environments and a heap.

\item \textbf{Higher-order Functions with Restricted Scopes} \( \ires \) supports
lambda functions as values but it has only restricted scopes. In each function,
only global variables, parameter, and newly defined local variables are accessible.
It means that the function closure does not capture the the current environment.
We use such restricted scopes because it is enough to represent abstract algorithms.

\item \textbf{Primitive Values} \( \ires \) supports ECMAScript primitive values except
the symbols that is newly introduced after ECMAScript 6. Thus, only five ECMAScript primitives
are defined in \( \ires \); numbers, strings, booleans, \( \code{undefined} \), and \( \code{null} \).
Moreover, \( \ires \) also supports the unique \( \code{absent} \) value to represent
the absence of parameters. For example, the second parameter \( \code{PreferredType} \)
of \( \code{ToPrimitive} \) algorithm in Figure~\ref{fig:to-primitive-es} might be
not present in some function calls. Then, the parameter has the \( \code{absent} \) value
to represent its absence.

\item \textbf{Abstract Data Types} \( \ires \) only supports three abstract data types;
\( \code{Record} \) for mapping from some values into other value,
\( \code{List} \) for sequential data types,
and \( \code{Singleton} \) for singleton data types.
They are stored in corresponding addresses in the heap structure.
For example, ECMAScript environment records are represented as \( \code{Record} \) data types
from String values for identifier names into addresses.
The addresses point to other \( \code{Record} \) data types that represent ECMAScript bindings.
We treat a ECMAScript constants such as \( \code{empty} \) and primitive symbols as singleton
data types in \( \ires \).
\end{itemize}

@@

To make easy write conversion rules, we support \textit{rule generation assistant}.
It consists of several helper functions to show the specific statistics of
the not yet convertible abstract algorithm steps. It make easy not only construct
conversion rules from the scratch but also update existing conversion rules
for updated specifications. We explain each helper function and how to utilize
it to construct conversion rules.

@@

\subsubsection{Fault localization based on \( \tstar \) tokens}

### 2019-08-15 icse/eval.tex
Written abstract

\begin{itemize}
  \item RQ1) Does ASE correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
    test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
  \item RQ2) Is endurable size of manual portion in implementation of ASE? \inred{refactoring for conversion rules / get statistics of conversion rules}
    개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
  \item RQ3) Does ASE deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
    각 feature name / 의미 / compile 성공률 / 결과 test
  \item RQ4) How many specification errors are detected by ASE? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
\end{itemize}

>>>>

\begin{itemize}
  \item RQ1) Does JSSET correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
    test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
  \item RQ2) Is endurable size of manual portion in implementation of JSSET? \inred{refactoring for conversion rules / get statistics of conversion rules}
    개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
  \item RQ3) Does JSSET deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
    각 feature name / 의미 / compile 성공률 / 결과 test
  \item RQ4) How many specification errors are detected by JSSET? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
\end{itemize}

### 2019-08-15 icse/framework.tex
Written abstract

In this section, we will demonstrate how our idea can be implemented to evaluate programming language. Although it is hard to generalize the process because the format of specification or 
environment of the programming language is varying, We shows the possibility to build entire system for evaluating target language with minimal human effort by giving end-to-end example of ECMAScript langauge.

\subsection{Extracting specification}
First step is to collect language specification and extract component that we can process autoamtically. For our target langauge, ECMAScript, has HTML format of specification in their website, and
in the specification they have BNF form of syntax, highly structured algorithm steps, and verbose texts to describe additional environment to evaluating ECMAScript source code.
We get these information by parsing HTML document, and passing these result to our previous moudle to get AST, Parser, and executable algorithms.

@@

\subsection{Generating initial environment for evaluating}
For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsincs. We will describe how to generate each component.

@@

 In specification, a built-in function object usually matches to abstract algorithm. Its algorithm name
 describes the hierarchy about object it should be contained. For example, there is an abstract algorithm named \( \code{ Object.prototype.propertyIsEnumerable } \). With its name,
 we can know that it corresponds to builtin function in the object \( \code{ Object.prototype } \) as attribute. 
 To support builtin object, we make structure of builtin object and its attributes.
 After we correctly organizes structure, then we made algorithm that autoamtically map corresponding field to the abstract algorithm in specification by matching its function name.

 \subsubsection{Intrinsics}

 While builtin objects has canonical name to refer itself in ECMAScript language, It is also frequently refered in specification. But name of builtin objects
 are defiend for reference in Host language, so it needs another name to refer it in specification langauge. For example, \( \code{Array} \) is a name for
 ECMAScript reference, so abstract algorithm should call \\
 \( \code{realm.[[GlobalObject]].[[GetOwnProperty]]("Array")} \) to get ECMAScript \( \code{Array} \) object. Instead of this verbose way, abstract algorithm intorduces intrinsics, which
are alias for built-in objects. For example it is refred as \( \code{\%Array\%} \) to refer Array Object.
 Map between Intrinsic name and Builtin objects are available in speicificaion as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.

@@

First, we categorized sections by types of algorithm.
Method-like abstract operation has seperate sections to describe it, so we manually add these sections to treat differently.
Also Syntax-directed operations are described in distinct sections, so both case is easy to extract it.
Rest algorithms are considered as ordinary Abstract operation.

@@

In this case, algorithm dispatching should consider receiver Object(i.e. \( \code{x.[[GetOwnProperty]](N)} \)).
For method-like abstract operation, we organized map from algorithm name to function for each type,
 and we insert functions as propertiy of object when such type of object is created. So In our example, when  \( \code{x} \) is created with Ordinary Object type,
 then we insert attributes with name \( \code{[[GetOwnProperty]]} \) and function from method-like abstract operation "[[GetOwnProperty]]" in Ordinary Object Internal method section, at the time of map creation.

@@

 Like Method-like abstract operation, many AST Value (in specification, it is called Parse Node) uses same name of algorithm but the content is differnt.
The most frequent example is Evaluation of the AST Value. Evaluation is described as \( \code{result of evaluating Expression} \), but Nonterminal
\( \code{ Expression } \) did not has specific algorithm \( \code{ Evaluation } \). Instead of this, some nonterminal that can be derived from \( \code{ Expression } \) has \( \code{ Evaluation }\),
(i.e. \( \code{ CallExpression } \)). Also in Syntax-directed operation, the subcomponent of AST can be used as values. For example, In the
Evaluation algorithm of\\ \( \code{CallExpression : CallExpression Arguments} \), algorithm can uses \( \code{CallExpression}\) or \( \code{Arguments}\) to refer subcomponent of AST.
 For Syntax-directed operation, we insert converted functions in AST structure, and add special expression to call Syntax-directed operation which requires AST Value and algorithm name.
We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.

>>>>

In this section, we will demonstrate how our idea can be implemented to evaluate programming language. Although it is hard to generalize the process because the format of specification or 
environment of the programming language is varying, We shows the possibility to build entire system for evaluating target language with minimal human effort by giving end-to-end example of ECMAScript language.

\subsection{Extracting specification}
First step is to collect language specification and extract component that we can process automatically. For our target language, ECMAScript, has HTML format of specification in their website, and
in the specification they have BNF form of syntax, highly structured algorithm steps, and verbose texts to describe additional environment to evaluating ECMAScript source code.
We get these information by parsing HTML document, and passing these result to our previous module to get AST, Parser, and executable algorithms.

@@

\subsection{Generating initial environment for evaluating}
For ECMAScript Specification, initial environment consists of the Builtin objects, Intrinsic objects. We will describe how to generate each component.

@@

 In specification, a built-in function object usually matches to abstract algorithm. Its algorithm name
 describes the hierarchy about object it should be contained. For example, there is an abstract algorithm named \( \code{ Object.prototype.propertyIsEnumerable } \). With its name,
 we can know that it corresponds to builtin function in the object \( \code{ Object.prototype } \) as attribute. 
 To support builtin object, we make structure of builtin object and its attributes.
 After we correctly organizes structure, then we made algorithm that automatically map corresponding field to the abstract algorithm in specification by matching its function name.

 \subsubsection{Intrinsic objects}

 While builtin objects has canonical name to refer itself in ECMAScript language, It is also frequently referred in specification. But name of builtin objects
 are defined for reference in Host language, so it needs another name to refer it in specification language. For example, \( \code{Array} \) is a name for
 ECMAScript reference, so abstract algorithm should call \\
 \( \code{realm.[[GlobalObject]].[[GetOwnProperty]]("Array")} \) to get ECMAScript \( \code{Array} \) object. Instead of this verbose way, abstract algorithm introduces Intrinsic objects, which
are alias for built-in objects. For example it is referred as \( \code{\%Array\%} \) to refer Array Object.
 Map between Intrinsic name and Builtin objects are available in specification as table form in section "6.1.7.4 Well-Known Intrinsic Objects", so we parse this table to generate global identifier to object.

@@

First, we categorized sections by types of algorithm.
Method-like abstract operation has separate sections to describe it, so we manually add these sections to treat differently.
Also Syntax-directed operations are described in distinct sections, so both case is easy to extract it.
Rest algorithms are considered as ordinary Abstract operation.

@@

In this case, algorithm dispatching should consider receiver Object(i.e. \( \code{x.[[GetOwnProperty]](N)} \)).
For method-like abstract operation, we organized map from algorithm name to function for each type,
 and we insert functions as property of object when such type of object is created. So In our example, when  \( \code{x} \) is created with Ordinary Object type,
 then we insert attributes with name \( \code{[[GetOwnProperty]]} \) and function from method-like abstract operation "[[GetOwnProperty]]" in Ordinary Object Internal method section, at the time of map creation.

@@

 Like Method-like abstract operation, many AST Value (in specification, it is called Parse Node) uses same name of algorithm but the content is different.
The most frequent example is Evaluation of the AST Value. Evaluation is described as \( \code{result of evaluating Expression} \), but Non-terminal
\( \code{ Expression } \) did not has specific algorithm \( \code{ Evaluation } \). Instead of this, some non-terminal that can be derived from \( \code{ Expression } \) has \( \code{ Evaluation }\),
(i.e. \( \code{ CallExpression } \)). Also in Syntax-directed operation, the sub-component of AST can be used as values. For example, In the
Evaluation algorithm of\\ \( \code{CallExpression : CallExpression Arguments} \), algorithm can uses \( \code{CallExpression}\) or \( \code{Arguments}\) to refer sub-component of AST.
 For Syntax-directed operation, we insert converted functions in AST structure, and add special expression to call Syntax-directed operation which requires AST Value and algorithm name.
We gather which AST can be applied to a function. Also, to use child node of AST, we passes child node of AST to function as argument.

### 2019-08-15 icse/intro.tex
Written abstract

However, the existing JavaScript foraml semantics are fully manually written
by researchers based on ECMAScript specifications. ECMAScript is a standardized language
of JavaScript and its specifications formally define its syntax and semantics.
As described in Figure~\ref{fig:previous}, former researchers implement parser and
describe semantics using their own intermediate representation (IR) according to the ECMAScript
specifications. However, their approaches are fully manual thus excessively labor-intensive
to handle full semantics.

Moreover, it is not suitable approach to cope with the updates of ECMAScript specifications.
Most of full formal semantics of ECMAScript only supports ECMAScript 5.1 that was
released in December 2009. Until 2014, it was not big deal because ECMAScript
specifications are rarely updated. However, in late 2014, The Ecma Technical
Committee 39 (TC39) decided to release ECMAScript on a yearly cadence. From the
ECMAScript 6, officially ECMAScript 2015, they updated specifications every years
in June. Now, no researches correctly deal with recent ECMAScript features;
lexical bindings (\( \code{let} \)), spread operator (\( \code{...} \)),
classes, for-of operators, async functions, or generators.

To alleviate such problems, we propose \textit{Automatic Semantics Extractor (ASE)}
for ECMAScript specifications. The tool automatically generates JavaScript parser
from syntax provided by ECMAScript specifications. It also extracts formal
JavaScript semantics in semi-automatic ways. It is semi-automatic because
it depends on manually defined \textit{conversion rules}. Each rule describes how abstract
algorithms in specifications are converted into functions of our core language \( \ires \).
However, to save the labor of defininig such rules, we also propose \textit{rule generation assistant}.
It suggests new conversion rules based on statistical analysis of not yet convertable algorithms.
The assistant helps us deal with changed or newly introduced algorithms defined in new versions of
ECMAScript specifications as well.

Our main contribution is our tool ASE that mechanizes extraction of JavaScript syntax and semantics
from ECMAScript specifications:
\begin{itemize}
  \item ASE enables to extract the syntax and semantics of ECMAScript 2019,
    which is the latest released version of ECMAScript in June 2019.
    Moreover, we successfully applied our tool into the next proposed version,
    ECMAScript 2020. The official conformance test suite, test262, provides
    \inred{XXXXX} tests for ECMAScript 2020 and we passed \inred{XXXXX} tests
    among them.
  \item ASE is also applicable in-process proposed langauge features in a modular way.
    ECMAScript specifications are open-source based documentations. Thus, anyone
    could propose some new language feautres. Then, the committee carefully inspects
    such proposals and adds them into specifications. Each in-process proposed language
    feature has its own specification and tests. Thus, we apply ASE into the specification
    and evalute the corresponding tests. Among \inred{XX} proposals, we successfully
    pass all the tests in \inred{XX} proposals and partially pass the tests in \inred{XX}
    proposals.
  \item Moreover, all extraction mechanisms in ASE is automatic thus we could use this tool
    to find possible specification errors. We found \inred{X} possible specification errors
    in ECMAScript 2019 and reported them into TC39, which is the Ecma Technical Committee.
    We confirm that all of them are real specification errors.
\end{itemize}

>>>>

However, the existing JavaScript formal semantics are fully manually written
by researchers based on ECMAScript specifications. ECMAScript is a standardized language
of JavaScript and its specifications formally define its syntax and semantics.
As described in Figure~\ref{fig:previous}, former researchers implement parser and
describe semantics using their own intermediate representation (IR) according to the ECMAScript
specifications. However, their approaches are fully manual thus excessively labor-intensive
to handle full semantics.

Moreover, it is not suitable approach to cope with the updates of ECMAScript specifications.
Most of full formal semantics of ECMAScript only supports ECMAScript 5.1 that was
released in December 2009. Until 2014, it was not big deal because ECMAScript
specifications are rarely updated. However, in late 2014, The Ecma Technical
Committee 39 (TC39) decided to release ECMAScript on a yearly cadence. From the
ECMAScript 6, officially ECMAScript 2015, they updated specifications every years
in June. Now, no researches correctly deal with recent ECMAScript features;
lexical bindings (\( \code{let} \)), spread operator (\( \code{...} \)),
classes, for-of operators, asynchronous functions \( \code{async} \), or generators.

To alleviate such problems, we propose JavaScript Semantics Extraction Toolchain (JSSET)
based on ECMAScript specifications. The tool automatically generates JavaScript parser
from syntax provided by ECMAScript specifications. It also extracts formal
JavaScript semantics in semi-automatic ways. It is semi-automatic because
it depends on manually defined \textit{conversion rules}. Each rule describes how abstract
algorithms in specifications are converted into functions of our core language \( \ires \).
However, to save the labor of defining such rules, we also propose \textit{rule generation assistant}.
It suggests new conversion rules based on statistical analysis of not yet convertible algorithms.
The assistant helps us deal with changed or newly introduced algorithms defined in new versions of
ECMAScript specifications as well.

Our main contribution is our tool JSSET that mechanizes extraction of JavaScript syntax and semantics
from ECMAScript specifications:
\begin{itemize}
  \item JSSET enables to extract the syntax and semantics of ECMAScript 2019,
    which is the latest released version of ECMAScript in June 2019.
    Moreover, we successfully applied our tool into the next proposed version,
    ECMAScript 2020. The official conformance test suite, test262, provides
    \inred{XXXXX} tests for ECMAScript 2020 and we passed \inred{XXXXX} tests
    among them.
  \item JSSET is also applicable in-process proposed language features in a modular way.
    ECMAScript specifications are open-source based documentations. Thus, anyone
    could propose some new language features. Then, the committee carefully inspects
    such proposals and adds them into specifications. Each in-process proposed language
    feature has its own specification and tests. Thus, we apply JSSET into the specification
    and evaluate the corresponding tests. Among \inred{XX} proposals, we successfully
    pass all the tests in \inred{XX} proposals and partially pass the tests in \inred{XX}
    proposals.
  \item Moreover, all extraction mechanisms in JSSET is automatic thus we could use this tool
    to find possible specification errors. We found \inred{X} possible specification errors
    in ECMAScript 2019 and reported them into TC39, which is the Ecma Technical Committee.
    We confirm that all of them are real specification errors.
\end{itemize}

### 2019-08-15 icse/main.tex
Written overview
Written abstract

\documentclass[sigconf,review]{acmart}

\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{listings}

@@

% 
\lstdefinestyle{ires}{
  frame=tb,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=fixed,
  basicstyle={\footnotesize\ttfamily},
  numbers=none,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  frame=single,
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3,
}

@@

\title{Automatic Extraction of JavaScript Formal Semantics
from ECMAScript Specifications}

@@

\maketitle
\begin{abstract}
\end{abstract}

% TODO \keywords

>>>>

\documentclass[sigconf,review,anonymous=true]{acmart}

\usepackage{kotex}
\usepackage[T1]{fontenc}
\usepackage{beramono}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{qtree}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}

@@

% ECMAScript Intermediate Reprentations
\lstdefinestyle{ires}{
  frame=tb,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=fixed,
  basicstyle={\footnotesize\ttfamily},
  numbers=none,
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  frame=single,
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3,
}

@@

\title{JSSET: JavaScript Semantics Extraction Toolchain}

@@

\begin{abstract}
While JavaScript is initially invented for client-side in web browsers,
JavaScript engines are now embedded in many other types of host software.
Despite its popularity, JavaScript semantics are complicated because of its
dynamic nature. Thus, the formal analysis and verification of JavaScript programs
require its formal semantics. Several researches proposed formal semantics
of JavaScript based on ECMAScript, the official specifications of JavaScript.
However, the existing approaches are fully manual and only target ECMAScript 5.1.
It is a critical problem to understand recent JavaScript programs
because ECMAScript is annually updated from 2015. Thus, already five more updates
after ECMAScript 5.1.

To alleviate such problems, we propose JSSET, a JavaScript Semantics Extraction
Toolchain. It automatically extracts JavaScript formal semantics from ECMAScript
specifications. JSSET generates JavaScript parser for the given grammar written
in \( \bnfes \), an extended BNF used in ECMAScript specifications.
Our tool also converts each abstract algorithm written in structured natural
languages into functions written in \( \ires \), an Intermediate Representation
for ECMAScript specifications. The conversion from algorithms to \( \ires \) functions
is defined with \textit{conversion rules}. We apply JSSET into the next proposed
version, ECMAScript 2020. and the extracted semantics passes all \inred{XXXXX} tests
in test262, the official ECMAScript conformance test suite.
Moreover, JSSET also successfully extracts semantics for \inred{XX} proposed features
by adding only \inred{XX} minor conversion rules.
\end{abstract}

\keywords{
  JavaScript,
  mechanized formal semantics,
  recursive descent parsing
}

\maketitle

### 2019-08-15 icse/overview.tex
Written abstract

In this section, we introduce the overall structure of ASE and the outline of
this paper. Figure~\ref{fig:overview} depicts the overall structure of ASE.
It mechanizes to extract syntax and semantics of ECMAScript using
two main module; the \textit{parser generator} and the \textit{algorithm compiler}.
If first extracts information via the spec extractor.
ECMAScript specifications are provided as a readable HTML file.
Thus, we develop the spec extractor in JavaScript to automatically
extract their contents.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{img/overview.png}
  \caption{Overall structure of Automatic Semantics Extractor (ASE)
  for ECMAScript specifications}
  \label{fig:overview}
\end{figure}

@@

From now, we describe the detailed techniques of ASE.
Section 3 formallly defines \( \bnfes \) and how to automatically
generate parsers from given \( \bnfes \) using lookahead parsers.
Section 4 explains abstract algorithms with tagged tokens
and how to compile them into \( \ires \) functions based on
given conversion rules. Section 5 describes the implemented details
about initial settings to evaluate JavaScript programs. Section 6
discusses the effectiveness of ASE with four research questions.
Section 7 discusses related work and Section 8 concludes.

>>>>

In this section, we introduce the overall structure of JSSET and the outline of
this paper. Figure~\ref{fig:overview} depicts the overall structure of JSSET.
It mechanizes to extract syntax and semantics of ECMAScript using
two main module; the \textit{parser generator} and the \textit{algorithm compiler}.
If first extracts information via the spec extractor.
ECMAScript specifications are provided as a readable HTML file.
Thus, we develop the spec extractor in JavaScript to automatically
extract their contents.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{img/overview.png}
  \caption{Overall structure of JavaScript Semantics Extraction Toolchain (JSSET)}
  \label{fig:overview}
\end{figure}

@@

From now, we describe the detailed techniques of JSSET.
Section 3 formallly defines \( \bnfes \) and how to automatically
generate parsers from given \( \bnfes \) using lookahead parsers.
Section 4 explains abstract algorithms with tagged tokens
and how to compile them into \( \ires \) functions based on
given conversion rules. Section 5 describes the implemented details
about initial settings to evaluate JavaScript programs. Section 6
discusses the effectiveness of JSSET with four research questions.
Section 7 discusses related work and Section 8 concludes.
